---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# azmapr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/azmapr)](https://CRAN.R-project.org/package=azmapr)
[![R-CMD-check](https://github.com/pitt-ptrc/azmapr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/pitt-ptrc/azmapr/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of azmapr is to access the Azure Maps API and tidy the results.

## Installation

You can install the development version of azmapr like so:

``` r
remotes::install_github("pitt-ptrc/azmapr")
```

## Example

Given data frame with a column `address`, the main wrapper function `azm_geocode` has sane defaults. 

```{r example}
library(azmapr)

azm_geocode(cand)
```

The Azure Maps API limits you to 100 address batches. If you pass a more than 100, `azmapr` breaks it up into chunks and pauses briefly in between. Azure Maps supports async geocoding for larger batches, but `azmapr` hasn't figured that out yet.

```{r}
azm_geocode(cand, .test_batch = TRUE)
```

If you want to adjust settings, the functions are pipe-able. 

```{r example-adjustment}

cand |> 
  azm_fmt_batch(address, limit = 2) |> 
  azm_request_batch(direction = "fwd") |> 
  azm_extract_body(type = "viewport", direction = "fwd") |> 
  dplyr::bind_rows() |> 
  dplyr::mutate(topLeftPoint = unlist(topLeftPoint),
                btmRightPoint = unlist(btmRightPoint))

```

You can also reverse geocode. Again, given a dataframe with `lat` and `lon` the main wrapper has sane defaults. Suppose you want to associate 9-digit zipcodes with coordinates. 

```{r}
coords |> 
  azm_rev_geocode(lat, lon) |> 
  dplyr::select(lat, lon, streetNameAndNumber, extendedPostalCode)
```

But you can also pipe and adjust

```{r}
coords |> 
  azm_fmt_rev_batch(lat, lon, limit = 1) |> 
  azm_request_batch(direction = "rev") |> 
  azm_extract_body(type = "address", direction = "rev") |> 
  dplyr::bind_rows()
```
